Topic modeling on EU and the USA research projects

### 2017-06-25 thesis_report/draft_thesis.tex
Future work

\begin{titlepage}
	\centering
	\includegraphics[width=0.8\textwidth]{figs/logo.jpg}\par\vspace{4cm}
	{\scshape\Large MSc thesis\par}
	\vspace{1.5cm}
	{\Large\bfseries Topic modeling on EU and the USA research projects\par}
	\vspace{2cm}
	{\Large Maria Iliadi\par}
	\vfill
	supervised by\par
	Prof.~Panos Louridas

@@

>>>>

\begin{titlepage}
	\centering
	\includegraphics[width=0.8\textwidth]{figs/logo.jpg}\par\vspace{4cm}
	{\scshape\Large MSc thesis\par}
	\vspace{1.5cm}
	{\Large\bfseries Topic modeling on EU and the USA research projects\par}
	\vspace{2cm}
	{\Large Maria Iliadi\par}
	\vfill
	supervised by\par
	Assoc.Prof.~Panos Louridas

@@

In future research, we intend to extend this work by exploring more complex
models. In the standard LDA model, both the order of the words and the order of
the documents are oblivious to the model. One future direction is to use a
Dynamic Topic Model\cite{Blei:2006:DTM:1143844.1143859}, in which the order of
the documents plays an important role. More precisely, the documents are grouped
by time slice (e.g. years) and it is assumed that the documents of each group
come from a set of topics that involved from the set of the previous slice.
Moreover, we are planning to examine further the importance of corpus
preprocessing in our dataset, in order to get higher quality topics.

Another possible future direction is to integrate other data sources to further
investigate the content and the evolution of the research topics. For example,
we could add the projects that got funded by NIH in USA and/or find projects
from other funding agencies, to measure the impact of new emerging topics.

Last but not least, it would be interesting to explore the correlation of the
topics with the countries/states that are involved in the projects, and address
question like "which countries in EU are mostly collaborate? on which topics"
and "which states of the US are getting more funding compared to others".
